\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Maninderpal Singh} \\ \vspace{1pt}
    % \small \href{tel:+91 12345 67890}{+91 12345 67890} $|$
    \href{mailto:msc24x@gmail.com}{\underline{msc24x@gmail.com}} $|$ 
    \href{https://cambo.in}{\underline{cambo.in (portfolio)}} $|$ 
    \href{https://github.com/msc24x}{\underline{github.com/msc24x}} $|$
    \href{https://linkedin.com/in/msc24x}{\underline{linkedin.com/in/msc24x}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Punjabi University}{89.8 Percentile}
      {Department of Statistics | B.Sc. in Computer Science, Statistics and Mathematics}{Jul. 2019 -- Jul. 2022}      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Instahyre}{Sep 2023 -- Present}
    {SDE I}{New Delhi, India}
    \resumeItemListStart
      \resumeItem{\textbf{Module Ownership: }Owned 4 platform modules at different stages, taking responsibility for feature development, bug resolution and performance optimizations.}
      \resumeItem{\textbf{Platform Reliability: }Resolved functional and performance issues across owned modules, cutting recurring bugs by 40\% in two quarters and boosting system stability and module reliability.}
      \resumeItem{\textbf{Product Collaboration: }Partnered closely with Product Managers and cross-functional teams to design and implement features across in-progress and existing modules, contributing to iterative product improvements and timely feature delivery.}
    \resumeItemListEnd

  \resumeSubheading
      {Buyceps}{Dec 2022 -- Sep 2023}
      {Software Engineer}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{\textbf{Backend Leadership: }Led backend development for Buyceps Marketplace, implementing unified authentication, order/shipment workflows, and core data models.}
        \resumeItem{\textbf{Search System: }Built an Algolia-powered product browser with optimized DB indexing and internal UI tools for fast, efficient search.}
        \resumeItem{\textbf{Performance Optimization: }Optimized major GraphQL resolvers and REST APIs, reducing N+1 queries and cutting SQL calls by 75\%.}
      \resumeItemListEnd

  \resumeSubheading
    {Studypaq}{Oct 2022 -- Dec 2022}
    {Software Engineer}{California, United States}
    \resumeItemListStart
      \resumeItem{\textbf{Security \& Performance: }Discovered and fixed a critical vulnerability in a paywall protected module.}
      \resumeItem{\textbf{API design: }Responsible of designing and developing core APIs and architecture. }
      \resumeItem{\textbf{Server performance: }Improved response time of high-traffic endpoints by ~47\%, reducing SSR latency.}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Hunter - Online contests hosting platform (SaaS)}}{Jan 2022 -- Sep 2022}
      \resumeProjectHeading{\href{https://github.com/msc24x/hunter}{\emph{\underline{Repository}}} Deployed at \href{https://hunter.cambo.in}{\emph{\underline{hunter.cambo.in}}}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Architecture: }Engineered a full-stack SaaS using Node.js (Express, TypeScript), Angular, MySQL.}
            \resumeItem{\textbf{Code Execution Engine: }Created my own containerized remote execution service using GoLang, RabbitMQ.}
            \resumeItem{\textbf{Deployment: }Deployed using NGINX on Azure VM, later migrating infrastructure to Oracle Cloud and PlanetScale; currently self-hosted on bare-metal homelab.}
          \resumeItemListEnd
          
    \resumeProjectHeading
          {\textbf{DinoPlusPlus - A Terminal Based C++ Game (ASCII Graphics)}}{Apr 2021 -- May 2021}
      \resumeProjectHeading{\href{https://github.com/msc24x/DinoPlusPlus}{\emph{\underline{Repository}}}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Gameplay Engine:} Built core gameplay, menu system, and animations from scratch without external libraries.}
            \resumeItem{\textbf{Rendering Optimization:} Resolved frame desynchronization by buffering frames before rendering.}
            \resumeItem{\textbf{Collision Detection:} Implemented real-time edge-based collision detection.}
          \resumeItemListEnd

    % \resumeProjectHeading
    %       {\textbf{BOP Music - Android Music Player}}{July 2021 -- Oct 2021}
    %   \resumeProjectHeading{\href{https://github.com/lscambo13/GrooveMusicClone}{\emph{\underline{Repository}}}}{}
    %       \resumeItemListStart
    %         \resumeItem{\textbf{UI/UX:} Built clean UI and smooth experience using motion layouts and following the principles of MVVM architecture}
    %         \resumeItem{\textbf{Data/services:} Implemented background player service with SQL room database}
    %       \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Contactless - WhatsApp’s API driven android app }}{Jul 2020 -- Aug 2020}
      \resumeProjectHeading{\href{https://github.com/lscambo13/ContactlessForWhatsApp}{\emph{\underline{Repository}}},       \href{https://forum.xda-developers.com/android/apps-games/5-0-contactless-whatsapp-t4151497}{\emph{\underline{XDA Forum}}}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Android app:} Developed UI/UX using Kotlin consuming Web API allowing users to chat with any contact}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages:} Python, TypeScript, JavaScript GoLang, C/C++, Bash \\
      \textbf{Tools/Frameworks:} Django, Angular, REST APIs, Git, Mercurial, NextJS, NodeJS, GraphQL \\
      \textbf{Databases:} MySQL, PostgreSQL, MongoDB \\
      \textbf{Cloud \& DevOps:} Docker, NGINX, Scripting, Azure, Oracle Cloud \\
      \textbf{Core Competencies:} System Design, Performance Engineering, Management, Scalability, AI
    }}
 \end{itemize}

%  %-----------LIBRARIES-----------
% \section{Packages Written}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%     \textbf{ \href{https://github.com/msc24x/xobserver}{\emph{\underline{XObserver}}} } {: An NPM package to enhance some subjective usage of IntersectionObserver API}
%    }}
% \end{itemize}

%-------------------------------------------
\end{document}